Status Update regarding \n Assessment of the KLGO coastal waterbird survey monitoring program

### 2020-06-16 analysis/paper/CCRPmarkdownExample.rmd
Added file as an example for NPS-CCRP

---
title: "Status Update regarding \n Assessment of the KLGO coastal waterbird survey monitoring program"
author:
- name: Joel H. Reynolds^[U.S. National Park Service, Alaska Region, Natural Resources
    Science Team]
- name: Madeleine Ward^[Swarthmore College, Dept. of Mathematics and Statistics]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::word_document2:
    fig_caption: yes
    toc: no
  pdf_document:
    fig_caption: yes
    toc: no
  word_document:
    toc: no
    fig_caption: true
    reference_docx: NRR_Author_Template_V4.2.docx
  html_document:
    df_print: paged
    fig_caption: yes
    number_sections: yes
    toc: no
editor_options: 
  chunk_output_type: inline
keywords: keyword 1; keyword 2; keyword 3
link-citations: yes
bibliography: KLGOCWS_References.bib
abstract: DRAFT ABSTRACT The Coastal Waterbird Survey has been conducted, with varying levels of
  effort and in-season frequency, since 2003 [@Surdyk2018]. The area of interest has
  been divided into eight contiguous survey units; on each survey, at each unit the
  number, age, composition (sex), breeding status, and noteworthy behavioral observations
  are recorded for each species [@Anonymous2009]. Given the constraints on personnel,
  time, and budgets, it is imperative that surveys be conducted efficiently in terms
  of both choice of sampling design and choice of sampling effort. Now that KLGO has
  multiple years of experience implementing the protocol, it is timely to step back
  and assess how things are going. We review the current program's objectives and survey design,
  identify statistical issues, and recommend potential solutions. Major topics include... etc. The study concludes with a series of recommended tasks that the park should
  undertake to improve the coastal waterbird survey's efficiency and effectiveness.
---

@@

```{r Fig-SpeciesTiming2, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.height=25, fig.width=12, fig.cap="For each of the target species, the dates on which they were observed in any of the sample areas."}

>>>>

---
title: "Status Update regarding \n Assessment of the KLGO coastal waterbird survey monitoring program"
author:
- name: Joel H. Reynolds^[U.S. National Park Service, Alaska Region, Natural Resources
    Science Team]
- name: Madeleine Ward^[Swarthmore College, Dept. of Mathematics and Statistics]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
    fig_caption: yes
    number_sections: yes
    toc: no
  pdf_document:
    fig_caption: yes
    toc: no
  word_document:
    toc: no
    fig_caption: true
    reference_docx: NRR_Author_Template_V4.2.docx
  bookdown::word_document2:
    fig_caption: yes
    toc: no
editor_options: 
  chunk_output_type: inline
keywords: keyword 1; keyword 2; keyword 3
link-citations: yes
bibliography: KLGOCWS_References.bib
abstract: DRAFT ABSTRACT The Coastal Waterbird Survey has been conducted, with varying levels of
  effort and in-season frequency, since 2003 [@Surdyk2018]. The area of interest has
  been divided into eight contiguous survey units; on each survey, at each unit the
  number, age, composition (sex), breeding status, and noteworthy behavioral observations
  are recorded for each species [@Anonymous2009]. Given the constraints on personnel,
  time, and budgets, it is imperative that surveys be conducted efficiently in terms
  of both choice of sampling design and choice of sampling effort. Now that KLGO has
  multiple years of experience implementing the protocol, it is timely to step back
  and assess how things are going. We review the current program's objectives and survey design,
  identify statistical issues, and recommend potential solutions. Major topics include... etc. The study concludes with a series of recommended tasks that the park should
  undertake to improve the coastal waterbird survey's efficiency and effectiveness.
---

@@

```{r Fig-SpeciesTiming2, echo=FALSE, eval=FALSE, cache=TRUE, fig.show= 'asis', fig.height=25, fig.width=12, fig.cap="For each of the target species, the dates on which they were observed in any of the sample areas."}
